---
title: "Setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GeneticMediation)
```


## Installation

You can install `GeneticMediation` from [GitHub](https://github.com/)
with:

``` r
# install.packages("devtools")
devtools::install_github("tydarnell/GeneticMediation")
```
## Prerequisites

``` r
####################################################################################
#   
#   Software:--------------------------------------------------------
#
#     R version >= 3.6.1
#     devtools (to install GeneticMediation package from github)
#     Rstudio  (highly recommended)
#
#   Data:------------------------------------------------------------
#
#     ROSMAP Study:**************************************************
#       ReadCounts.csv   
#       H3K9acDomains.csv 
#
#     UNC Wu Lab:****************************************************
#       snps.txt
#       JulyselGeneBySNP.1030.RData
#       mediator_chr#_new.RData (each chr has a separate RData file)
#
####################################################################################
```
## Data Access

* The [ROSMAP](https://www.synapse.org/#!Synapse:syn3219045) data can be obtained from [Synapse](https://www.synapse.org/#!Synapse:syn3219045). Read instructions for [data access](https://adknowledgeportal.synapse.org/DataAccess/Instructions)

* The [UNC Wu Lab](http://diwulab.web.unc.edu/) data requires permission from Dr. Di Wu

## Setup

1)  Create an Rproject in Rstudio


2)  Install and load `GeneticMediation` from
    [GitHub](https://github.com/) with:

<!-- end list -->

``` r
# devtools::install_github("tydarnell/GeneticMediation")
library(GeneticMediation)
```


3)  Create subdirectories of your Rproject directory: data, data/mediator, results with:

<!-- end list -->

``` r
GeneticMediation::setup_folders()
```


4)  Put all data except for the `mediator_chr#_new.RData` files in the
    data folder


5)  Put the `mediator_chr#_new.RData` files in the mediator folder


6)  Check that data files are in the data folder with:

<!-- end list -->

``` r
GeneticMediation::check_data()
```
